Face Attractiveness and the Sense of Reality

### 2022-09-08 analysis.Rmd
script

df <- read.csv("data/data.csv")
# |>
#   mutate(
#     Date = lubridate::dmy(Date),
#     Participant = fct_reorder(Participant, Date),
#     Screen_Refresh = as.character(Screen_Refresh),
#     Illusion_Side = as.factor(Illusion_Side),
#     # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
#     Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
#     Block = as.factor(Block),
#     Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
#   )
```

@@

```{r message=FALSE, warning=FALSE}
outliers <- c()
```

@@

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, starts_with("Attention"), starts_with("Duration")) |>
  slice(1) |>
  ungroup() |>
  rowwise() |> 
  mutate(Attention_Check = mean(c(Attention_Check1, Attention_Check2, Attention_Check3))) |> 
  ungroup() |> 
  arrange(Attention_Check)
```

@@

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
  rbind(dfsub) |>
  mutate(Attention_Check = paste0(
    insight::format_value(Attention_Check, 1), 
    " (", insight::format_value(Attention_Check1, 0), 
    ", ",
    insight::format_value(Attention_Check2, 0), 
    ", ",
    insight::format_value(Attention_Check3, 0),
    ")")) |> 
  select(-Attention_Check1, -Attention_Check2, -Attention_Check3) |> 
  datawizard::data_relocate("Attention_Check", 2) |> 
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |>
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A")
```

```{r message=FALSE, warning=FALSE}
p_att <- dfsub |>
  select(Participant, starts_with("Att")) |> 
  pivot_longer(-Participant) |> 
  # mutate(name = str_remove(name, "Cor_")) |> 
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
  scale_color_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
  see::theme_modern() +
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        legend.position = "top") +
  labs(y = "Score", fill="") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

p_time <- dfsub |>
  select(Participant, starts_with("Duration")) |> 
  pivot_longer(-Participant) |> 
  mutate(name = str_remove(name, "Duration_")) |> 
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("#4CAF50", "#FF9800")) +
  scale_color_manual(values = c("#4CAF50", "#FF9800")) +
  see::theme_modern() +
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        legend.position = "top") +
  labs(y = "Duration (min)", fill="") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

p_cor <- dfsub |>
  select(Participant, starts_with("Cor")) |> 
  pivot_longer(-Participant) |> 
  mutate(name = str_remove(name, "Cor_")) |> 
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("#F44336", "#9C27B0")) +
  scale_color_manual(values = c("#F44336", "#9C27B0")) +
  see::theme_modern() +
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        legend.position = "top") +
  labs(y = "Correlation", fill="") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

(p_att + theme(axis.text.x = element_blank())) / 
  (p_time + theme(axis.text.x = element_blank())) /
  (p_cor)
```

@@

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, Age, Sex, Sexual_Orientation, Ethnicity, Education, Nationality, Device_OS, starts_with("Screen")) |>
  slice(1) |>
  ungroup()
```

@@

plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size=3) {
  library(emojifont)
  ggwaffle::waffle_iron(dfsub, what, rows = rows) |>
    # mutate(label = emojifont::fontawesome('fa-smiley')) |>
    # mutate(label = emojifont::emoji('smiley')) |>
    ggplot(aes(x, y)) +
    geom_point(aes(color = group), shape = "square", size=size) +
    # ggwaffle::geom_waffle(color = "white") +
    # geom_point() +
    # geom_text(aes(color=group ,label=label), family='fontawesome-webfont', size=4) +
    # geom_text(aes(color=group ,label=label), family='EmojiOne', size=4) +
    coord_equal() +
    ggtitle(title) +
    labs(fill = "", color = "") +
    # scale_x_continuous(expand = c(0, 0)) +
    # scale_y_continuous(expand = c(0, 0)) +
    theme_void() +
    # ggwaffle::theme_waffle() +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}
```

```{r fig.width=20, fig.height=15}
# p1 <- plot_distribution(dfsub, "Age", fill = "#FF9800")
# p2 <- plot_distribution(dfsub, "Duration", title = "Total Duration", subtitle = "in minutes", fill = "#F44336")
# p3 <- plot_distribution(dfsub, "Break_Duration", title = "Break Duration", subtitle = "in minutes", fill = "#3F51B5")

p4 <- plot_waffle(dfsub, "Sex") +
  scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63", "Other" = "#FF9800"))

p5 <- plot_waffle(dfsub, "Sexual_Orientation")

p5 <- plot_waffle(dfsub, "Education") +
  scale_fill_viridis_d()

p6 <- plot_waffle(dfsub, "Nationality") +
  scale_fill_manual(values = c("South American" = "#FF5722", "Middle Eastern" = "#FF9800", "Western" = "#2196F3", "Eastern" = "#673AB7", "African" = "#4CAF50", "South African" = "#009688"))

p7 <- plot_waffle(dfsub, "Ethnicity") +
  scale_fill_manual(values = c("Latino" = "#FF5722", "Asian" = "#FF9800", "Caucasian" = "#2196F3", "African" = "#4CAF50", "Jewish" = "#9C27B0", "Mixed" = "#795548"))

p8 <- plot_waffle(dfsub, "Screen_Resolution", title = "Screen Resolution") +
  scale_fill_pizza_d() +
  guides(fill = "none")

p9 <- plot_waffle(dfsub, "Device_OS", title = "Device OS") +
  scale_fill_bluebrown_d()

@@

# (p1 / p2 / p3) | (p4 / p5 / p9) | (p6 / p7 / p8)
```

## Results

### Manipulation Check

```{r message=FALSE, warning=FALSE}
df |>
  # mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
  #   summarize(Real = mean(Real)) |>
  #   ungroup() |>
  #   arrange(Real) |>
  #   pull(Participant))) |>
  mutate(Participant = fct_relevel(Participant, dfsub$Participant)) |> 
  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(
    limits = c(0, 1),
    expand = c(0, 0),
    breaks = c(0, 0.5, 1),
    label = c("Fake", "0", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

@@

```{r message=FALSE, warning=FALSE}
IVs <- c("Attractive", "Trustworthy", "Approachable", "Familiar", "Similar")

preds <- data.frame()
dats <- data.frame()
for(x in IVs) {
  for(y in IVs) {
    if(x == y) next
    print(paste(y, "~", x))
    model <- glmmTMB::glmmTMB(as.formula(
      paste(y, "~", x, " * Stimulus_SameSex + (1|Participant) + (1|Stimulus)")), 
      data = df, 
      family=glmmTMB::beta_family()
      )

@@

    pred <- estimate_relation(model, at=c(x, "Stimulus_SameSex"), length=20)
    pred$y <- y
    pred <- data_rename(pred, x, "Score")
    pred$x <- x
    preds <- rbind(preds, pred)

    dats <- rbind(dats, data.frame(Score = df[[x]], Predicted = df[[y]], x=x, y=y))
  }
}

@@

```{r message=FALSE, warning=FALSE}
dats |> 
  ggplot(aes(x = Score, y = Predicted)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_ribbon(data=preds, aes(ymin = CI_low, ymax = CI_high, group=Stimulus_SameSex), alpha = 0.3) +
  geom_line(data=preds, aes(color=Stimulus_SameSex)) +
  scale_fill_gradientn(colors=c("white", "#FF9800", "#F44336"), guide="none") +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_continuous(expand=c(0, 0)) +
  facet_grid(y~x, switch = "both") +
  theme_modern() +
  labs(title = "Collinearity in the Stimuli Ratings") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(face="bold", hjust=0.5)
  ) +
  ggside::geom_xsidedensity(fill = "grey", color="white") +
  ggside::geom_ysidedensity(fill = "grey", color="white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all") 
```

### Reality and Attractiveness

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Real ~ poly(Attractive, 2) + poly(Trustworthy, 2) +
                            (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())
model <- mgcv::gamm(Real ~ s(Attractive) + Trustworthy, random = list(Participant=~1, Stimulus=~1), data = df, family=mgcv::betar())

parameters::parameters(model)
```

```{r message=FALSE, warning=FALSE}
pred <- estimate_relation(model, at = c("Attractive"), length=20)

df |> 
  ggplot(aes(x = Attractive, y = Real)) +
  ggside::geom_xsidedensity(fill = "grey", color="white") +
  ggside::geom_ysidedensity(fill = "grey", color="white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_point2(alpha=0.25, size=4, color="white") +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted)) +
  scale_fill_viridis_c(guide="none") +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_continuous(expand=c(0, 0))

pred <- estimate_relation(model, at = c("Trustworthy"), length=20)

df |> 
  ggplot(aes(x = Trustworthy, y = Real)) +
  ggside::geom_xsidedensity(fill = "grey", color="white") +
  ggside::geom_ysidedensity(fill = "grey", color="white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_point2(alpha=0.25, size=4, color="white") +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted)) +
  scale_fill_viridis_c(guide="none") +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_continuous(expand=c(0, 0))
```

>>>>

df <- read.csv("data/data.csv") |>
  mutate(
    Date = lubridate::dmy(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    # Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other"),
    Belief = fct_relevel(Belief, "Fake", "Real"),
    Stimulus_Interest = case_when(
      Sexual_Orientation == "Heterosexual" & Stimulus_SameSex == "Opposite" ~ TRUE,
      Sexual_Orientation == "Heterosexual" & Stimulus_SameSex == "Same" ~ FALSE,
      Sexual_Orientation == "Homosexual" & Stimulus_SameSex == "Opposite" ~ FALSE,
      Sexual_Orientation == "Homosexual" & Stimulus_SameSex == "Same" ~ TRUE,
      Sexual_Orientation == "Bisexual" ~ TRUE,
      TRUE ~ NA
    )
  )

# head(df[is.na(df$Stimulus_Attract), ])

# Create individual scores for Simulation Monitoring
df <- df |>
  group_by(Participant, Belief) |>
  summarise(Confidence = mean(abs(Belief_Confidence)),
            n = n() / 109) |> 
  pivot_wider(names_from = "Belief", values_from = c("Confidence", "n")) |>
  ungroup() |> 
  merge(df, by = "Participant")
```

@@

```{r message=FALSE, warning=FALSE}
outliers <- c(
  # Very short duration for questionnaire in particular + low rating correlations
  "5eaef8702b68455d6e130595_ptsga"
  )
outliers_partial <- c(
  "5c6414540821d30001046198_x9q7r",
  "60dd7b03f1e72d38230df476_9yh9n")
```

@@

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, starts_with("Attention"), starts_with("Duration"), n_Fake) |>
  slice(1) |>
  ungroup() |>
  rowwise() |>
  mutate(Attention_Check = mean(c(Attention_Check1, Attention_Check2, Attention_Check3))) |>
  ungroup() |>
  arrange(Attention_Check)
```

@@

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
  rbind(dfsub) |>
  mutate(Attention_Check = paste0(
    insight::format_value(Attention_Check, 1),
    " (", insight::format_value(Attention_Check1, 1),
    ", ",
    insight::format_value(Attention_Check2, 1),
    ", ",
    insight::format_value(Attention_Check3, 1),
    ")"
  )) |>
  select(-Attention_Check1, -Attention_Check2, -Attention_Check3) |>
  datawizard::data_relocate("Attention_Check", 2) |>
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |>
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A") |> 
  kableExtra::row_spec(which(dfsub$Participant %in% outliers_partial) + 1, background = "#FFCC80")
```

```{r message=FALSE, warning=FALSE}
p_att <- dfsub |>
  select(Participant, starts_with("Att")) |>
  pivot_longer(-Participant) |>
  # mutate(name = str_remove(name, "Cor_")) |>
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
  scale_color_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
  see::theme_modern() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top"
  ) +
  labs(y = "Score", fill = "") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x = after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

p_time <- dfsub |>
  select(Participant, starts_with("Duration")) |>
  pivot_longer(-Participant) |>
  mutate(name = str_remove(name, "Duration_")) |>
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("#4CAF50", "#FF9800")) +
  scale_color_manual(values = c("#4CAF50", "#FF9800")) +
  see::theme_modern() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top"
  ) +
  labs(y = "Duration (min)", fill = "") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x = after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

p_cor <- dfsub |>
  select(Participant, starts_with("r_")) |>
  pivot_longer(-Participant) |>
  mutate(name = str_remove(name, "r_")) |>
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
  scale_color_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
  see::theme_modern() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, 
                               color = ifelse(levels(dfsub$Participant) %in% outliers, "red", ifelse(levels(dfsub$Participant) %in% outliers_partial, "orange", "black"))),
    legend.position = "top"
  ) +
  labs(y = "Correlation", fill = "") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x = after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

(p_att + theme(axis.text.x = element_blank())) /
  (p_time + theme(axis.text.x = element_blank())) /
  (p_cor)

df <- df |> 
  filter(!Participant %in% outliers)
```

@@

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, Age, Sex, Sexual_Orientation, Ethnicity, Education, Nationality, Device_OS, starts_with("Screen"), starts_with("IPIP"), starts_with("Social_"), starts_with("FFNI_"), starts_with("GPTS_"), starts_with("IUS_"), starts_with("SelfAttractiveness"), starts_with("AI"), n_Real, Confidence_Fake, Confidence_Real) |>
  slice(1) |>
  ungroup()
```

@@

plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size = 3) {
  # library(emojifont)
  ggwaffle::waffle_iron(dfsub, what, rows = rows) |>
    # mutate(label = emojifont::fontawesome('fa-smiley')) |>
    # mutate(label = emojifont::emoji('smiley')) |>
    ggplot(aes(x, y)) +
    geom_point(aes(color = group), shape = "square", size = size) +
    # ggwaffle::geom_waffle(color = "white") +
    # geom_point() +
    # geom_text(aes(color=group ,label=label), family='fontawesome-webfont', size=4) +
    # geom_text(aes(color=group ,label=label), family='EmojiOne', size=4) +
    coord_equal() +
    ggtitle(title) +
    labs(fill = "", color = "") +
    # scale_x_continuous(expand = c(0, 0)) +
    # scale_y_continuous(expand = c(0, 0)) +
    theme_void() +
    # ggwaffle::theme_waffle() +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}
```

```{r fig.width=20, fig.height=15}
p1 <- estimate_density(dfsub$Age) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(fill = "#FF9800")

p2 <- plot_waffle(dfsub, "Sex") +
  scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63", "Other" = "#FF9800"))

p3 <- plot_waffle(dfsub, "Sexual_Orientation")

p4 <- plot_waffle(dfsub, "Education") +
  scale_fill_viridis_d()

p5 <- plot_waffle(dfsub, "Nationality") +
  scale_fill_manual(values = c("South American" = "#FF5722", "Middle Eastern" = "#FF9800", "Western" = "#2196F3", "Eastern" = "#673AB7", "African" = "#4CAF50", "South African" = "#009688"))

p6 <- plot_waffle(dfsub, "Ethnicity") +
  scale_fill_manual(values = c("Latino" = "#FF5722", "Asian" = "#FF9800", "Caucasian" = "#2196F3", "African" = "#4CAF50", "Jewish" = "#9C27B0", "Mixed" = "#795548"))

p7 <- plot_waffle(dfsub, "Screen_Resolution", title = "Screen Resolution") +
  scale_fill_pizza_d() +
  guides(fill = "none")

p8 <- plot_waffle(dfsub, "Device_OS", title = "Device OS") +
  scale_fill_bluebrown_d()

@@

patchwork::wrap_plots(list(p1, p2, p3, p4, p5, p6, p7, p8))
```

# Results

## Manipulation Check

### Real / Fake

```{r message=FALSE, warning=FALSE}
# plot(estimate_density(filter(df, Participant == "60dd7b03f1e72d38230df476_9yh9n")$Belief_Answer))

df |>
  mutate(Participant = fct_relevel(Participant, df |> 
    group_by(Participant) |>
    summarize(Belief_Answer = mean(Belief_Answer)) |>
    ungroup() |>
    arrange(Belief_Answer) |>
    pull(Participant) |>
    as.character())) |>
  # mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |>
  ggplot(aes(x = Belief_Answer, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(0.5, 0.5)) +
  scale_x_continuous(
    limits = c(-1, 1),
    expand = c(0, 0),
    breaks = c(-1, 0, 1),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

@@

```{r message=FALSE, warning=FALSE}
IVs <- c("Attractive", "Goodlooking", "Trustworthy", "Familiar")

preds <- data.frame()
dats <- data.frame()
for (x in IVs) {
  for (y in IVs) {
    if (x == y) next
    print(paste(y, "~", x))
    model <- glmmTMB::glmmTMB(as.formula(
      paste(y, "~", x, "* Sex * Stimulus_SameSex + (1|Participant) + (1|Stimulus)")
    ),
    data = df,
    family = glmmTMB::beta_family()
    )

@@

    pred <- estimate_relation(model, at = c(x, "Stimulus_SameSex", "Sex"), length = 20)
    pred$y <- y
    pred <- data_rename(pred, x, "Score")
    pred$x <- x
    preds <- rbind(preds, pred)

    dats <- rbind(dats, data.frame(Score = df[[x]], Predicted = df[[y]], x = x, y = y))
  }
}

@@

```{r message=FALSE, warning=FALSE}
dats |>
  ggplot(aes(x = Score, y = Predicted)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  # geom_ribbon(data = preds, aes(ymin = CI_low, ymax = CI_high, group = Stimulus_SameSex), alpha = 0.3) +
  geom_line(data = preds, aes(color = Sex, linetype=Stimulus_SameSex)) +
  scale_fill_gradientn(colors = c("white", "#FF9800", "#F44336"), guide = "none") +
  scale_color_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  facet_grid(y ~ x, switch = "both") +
  theme_modern() +
  labs(title = "Collinearity in the Stimuli Ratings") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "grey", color = "white") +
  ggside::geom_ysidedensity(fill = "grey", color = "white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all")
```

### Effect of Delay

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Belief ~ poly(Delay, 2) + (1|Participant) + (1|Stimulus),
      data = df,
      family = "binomial"
    )
pred <- estimate_relation(model, at = "Delay", length = 20)

m_conf <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief / poly(Delay, 2) + (1|Participant) + (1|Stimulus),
      data = df,
      family = glmmTMB::beta_family()
    )
y_conf <- estimate_relation(m_conf, at = c("Delay", "Belief"), length = 20)
y_conf <- y_conf |> 
  mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range=c(0, 1), to=c(0.5, 1)), datawizard::rescale(x, range=c(1, 0), to=c(0, 0.5))))

df |>
  ggplot(aes(x = Delay, y = Real)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  # geom_ribbon(data=y_conf, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_line(data=y_conf, aes(y=Predicted, group=Belief), linetype = "dashed") +
  geom_ribbon(data=pred, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_line(data=pred, aes(y=Predicted), color="red") +
  scale_fill_gradientn(colors = c("white", "#795548"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_modern() +
  labs(title = "Effect of Re-exposure Delay", x = "Minutes") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "#795548", color = "white") +
  ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all")
```

## Determinants of Reality

```{r message=FALSE, warning=FALSE}
make_model <- function(df, var = "Attractive", formula=var, fill = "#2196F3") {
  m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", formula)),
                             data = df,
                             family = "binomial")
  y_real <- estimate_relation(m_real, at = c(var, "Sex"), length = 20)

  m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief /", formula)),
        data = df,
        family = glmmTMB::beta_family()
      )
  y_conf <- estimate_relation(m_conf, at = c(var, "Belief", "Sex"), length = 20)
  y_conf <- y_conf |> 
    mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range=c(0, 1), to=c(0.5, 1)), datawizard::rescale(x, range=c(1, 0), to=c(0, 0.5))))

  p <- df |>
    ggplot(aes_string(x = var, y = "Real")) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
    scale_fill_gradientn(colors = c("white", fill), guide = "none") +
    ggnewscale::new_scale_fill() +
    geom_hline(yintercept = 0.5, linetype = "dotted") +
    # geom_point2(alpha = 0.25, size = 4, color = "black") +
    geom_line(data=y_conf, aes(y=Predicted, group=interaction(Belief, Sex), color=Sex), linetype="dashed") +
    geom_ribbon(data = y_real, aes(y = Predicted, group=Sex, fill=Sex, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
    geom_line(data = y_real, aes(y = Predicted, color=Sex)) +

    scale_color_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_fill_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
    scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
    theme_modern(axis.title.space=0) + 
    ggside::geom_xsidedensity(fill = fill, color = "white") +
    ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
    ggside::theme_ggside_void() +
    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
    ggside::scale_xsidey_continuous(expand = c(0, 0))

  list(p=p)
}
```

```{r message=FALSE, warning=FALSE}
rez_at <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Attractive, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
                     var="Attractive", fill = "#F44336")
rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Goodlooking, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
                     var="Goodlooking", fill = "#E91E63")
rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Trustworthy, 2) * Sex + Goodlooking + (1|Participant) + (1|Stimulus)", 
                     var="Trustworthy", fill = "#4CAF50")
rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Familiar, 2) * Sex + (1|Participant) + (1|Stimulus)", 
                     var="Familiar", fill = "#2196F3")

(rez_at$p +
  theme(axis.text.x = element_blank()) +
  labs(x = "Attractiveness") |
rez_gl$p +
  labs(x = "Beauty") +
  theme(axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
) / 
(rez_tr$p +
  labs(x = "Trustworthiness") |
rez_fa$p +
  labs(x = "Familiarity") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())
) + 
  plot_annotation(title = "Determinants of Reality Beliefs", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5))) +
  plot_layout(guides = "collect")
```

## Interaction

```{r message=FALSE, warning=FALSE}
cor_test(dfsub, "SelfAttractiveness1", "SelfAttractiveness2")

df$Self_Attractiveness <- rowMeans(df[c("SelfAttractiveness1", "SelfAttractiveness2")])

```

## Inter-Individual Correlates

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Belief ~ 1 + (1|Participant) + (1|Stimulus), data=df, family="binomial")
dfsub <- modelbased::estimate_grouplevel(model) |> 
  filter(Group == "Participant") |> 
  transmute(Participant = Level, Simulation_Monitoring=Coefficient) |> 
  merge(dfsub, by="Participant")

model <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief + (Belief|Participant) + (1|Stimulus), data=df, family=glmmTMB::beta_family())
dfsub <- modelbased::estimate_grouplevel(model) |> 
  filter(Group == "Participant") |> 
  transmute(Participant = Level, Parameter, Coefficient) |> 
  pivot_wider(names_from = "Parameter", values_from = "Coefficient") |> 
  transmute(Participant, Confidence_Real_Model = BeliefReal, Confidence_Fake_Model = `(Intercept)`) |> 
  merge(dfsub, by="Participant")
```
```{r message=FALSE, warning=FALSE}
correlation::correlation(dfsub[c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model")], 
                         dfsub[c("Confidence_Fake", "Confidence_Real", "n_Real")],
                         )
```

### IPIP-6

```{r message=FALSE, warning=FALSE}
make_correlation <- function(x, y) {
  cor <- correlation::correlation(x,
    y,
    bayesian = TRUE,
    bayesian_prior = "medium.narrow",
    sort = TRUE
  ) |>
    datawizard::data_remove(c("ROPE_Percentage"))
  cor$`BF (Spearman)` <- format_bf(
    correlation::correlation(
      x, y,
      bayesian = TRUE,
      ranktransform = TRUE,
      bayesian_prior = "medium.narrow"
    )$BF,
    name = NULL, stars = TRUE
  )
  cor |>
    arrange(desc(BF))
}

sr <- c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model", "Confidence_Fake", "Confidence_Real", "n_Real")

r <- make_correlation(dfsub[sr], select(dfsub, starts_with("IPIP")))
filter(r, BF > 1)
```

### AI

```{r message=FALSE, warning=FALSE}
rez <- parameters::n_factors(select(dfsub, starts_with("AI")))
plot(rez)
